\documentclass{resume}
\usepackage{graphics}

\name{Jahziah Wagner}
\address{ +46 (0)760-335 220 \\ jahziah@bytelope.com }
\address{ Bytelope AB \\ Bennebolsgatan 14 \\ 163 50 Spånga, Stockholm }

\begin{document}
  \begin{rSection}{Experience}
      \begin{rSubsection}{Kindred People AB}{August 2021 - Present}{Pay and Withdraw Experience - Software developer}{Stockholm}
      \item Developing and maintaining payment service provider (PSP) integrations for deposits and withdrawals through payment providers such Adyen, Brite, Earthport, Swish, Trustly, Worldpay across the various brands and sites at Kindred such as Unibet, Mario Casino, Ottokasino and others. 
      \item Working regularly as incident manager in charge of monitoring and responding to incidents when they occur and taking any necessary steps to restore service and return normal business operations.
      \item \textbf{Keywords:} Java 17, Spring Boot, Kubernetes, Docker, Oracle Database, Solace PubSub+ Event Broker, Splunk, Okta, JMS, React, Unix.
    \end{rSubsection}
    
    \begin{rSubsection}{Svensk Travsport AB}{June 2020 - March 2021}{Backend - Lead developer}{Stockholm}
      \item Lead the development of backend APIs for horse racing in a team of software specialists using agile methods.
      \item Guided transition from outsourced software development to in-house software development.
      \item Cultivated a democratic decision-making process where each team member was involved.
      \item Streamlined handling of roughly 100 repositories for microservices.
      \item Effectivized use of overseas consultants.
      \item Delivered the new gallop web API for www.svenskgalopp.se successfully.
      \item \textbf{Keywords:} Java 11, Spring Boot, Kubernetes, Docker, Google Cloud Platform (GCP), Oracle Database, Unix.
    \end{rSubsection}

    \begin{rSubsection}{Combitech AB}{March 2020 - June 2020}{Commute Logger - Software developer}{Stockholm}
      \item Developed a feature-rich mobile app for tracking daily commute to and from work, comparing offices and carpooling.
      \item This project was conceived by the environmental manager with the aim of reducing carbon footprints.
      \item \textbf{Keywords:} Java 11, Spring Boot, Azure, Docker, OAuth2, PostgreSQL, Vue.js, Unix.
    \end{rSubsection}

    \begin{rSubsection}{Ericsson AB}{March 2019 - January 2020}{Guided Sales Digital Platform - Software developer}{Stockholm}
      \item Developed sales configuration tool "Guided Sales Digital Platform (GSDP)" for LTE \& 5G in a medium sized team using agile methods.
      \item \textbf{Keywords:} Java 11, Spring Boot, Azure, CosmosDB, Docker, Neo4j, OAuth2, PostgreSQL, Vue.js, Enterprise Architect, Unix.
    \end{rSubsection}

    \begin{rSubsection}{Inera AB }{November 2018 - February 2019}{Hjälpmedelstjänsten 2.0 - Data migration engineer}{Stockholm}
      \item Hjälpmedelstänsten is a comprehensive information service for assistive products in Sweden.
      It catalogs more than 450,000 assistive products and enables healthcare authorities to document
      information from agreements they have signed with each other.
      \item The database consists of categories based on the standard "Assistive products for persons with disability — Classification and terminology (ISO 9999)"
      \item Hjälpmedelstjänsten is aimed at regions, municipalities and suppliers of assistive products.
      \item Parts of the information stored in Hjälpmedelstjänsten is also made available to residents at 1177.se.
      \item Established a continuous data migration process which allowed for the successful delivery of the project:
       - Extracted large amounts of disparate data received at various points in time. \\
       - Provided decision support for operations managers with in-depth analysis of data, identifying issues and proposing solutions. \\
       - Provided migration support to software developers and testers.
      \item \textbf{Keywords:} Java 11, WildFly, Thorntail, Elasticsearch, OpenShift, Docker, Amazon S2, ETL, Git, H2, Maven, MySQL, React, Unix.
      \item \textbf{Web:} https://bitbucket.org/ineraservices/hjalpmedelstjansten
    \end{rSubsection}

    \begin{rSubsection}{Saab AB}{February 2017 - April 2018}{9LV CMS - Software Developer}{Järfälla}
      \item Developed a subsystem for a naval management system in a small self-organized team using agile methods.
      \item Managed sprint backlog, sprint planning and was team representative at Scrum of Scrums.
      \item Responsibilities included architecture, design, implementation, verification and documentation.
      \item \textbf{Keywords:} Java 8, Docker, MongoDB, JMS, ESB, Kerberos, LDAP, ANTLR4, Bash, C++, Golang, Python, Linux.
    \end{rSubsection}

    \begin{rSubsection}{Pierce AB}{August 2016 - December 2016}{E-commerce platform - Software developer}{Stockholm}
      \item Developed e-commerce platform in a small team using agile methods.
      \item Extended REST API with product information, prices and full text queries using Elasticsearch.
      \item Created a comprehensive set of API load tests with JMeter.
      \item \textbf{Keywords:} Java EE, Payara, Elasticsearch, Microsoft SQL Server, JMS, Play Framework, JMeter, Linux.
    \end{rSubsection}

    \begin{rSubsection}{Saab AB}{March 2012 - August 2016}{Mission data management - Software developer}{Järfälla}
      \item Developed software for the production of electronic warfare libraries for air, land and sea-based defence systems with high requirements on function and reliability in a medium-sized team using agile methods.
      \item Duties included requirements analysis, design, implementation, verification, delivery and documentation.
      \item Contributed to multiple projects with extensive customer contact.
      \item Served as technical design authority from 2013 to 2015.
      \item Consulted as on-site specialist with customer from September 2013 to June 2014.
      \item Parental leave from October 2015 to May 2016.
      \item \textbf{Keywords:} Java EE, JBoss EAP, WildFly, DB2, H2, JMS, Maven.
    \end{rSubsection}

    \begin{rSubsection}{Innventia AB}{February 2012 - July 2012}{PPA Carbon Calculator - Software developer}{Stockholm}
      \item Expanded the PPA Carbon Calculator to include:\\
      - Administration of office data and journalism data. \\
      - Submission and calculation of journalism impacts.\\
      - Submission and calculation of online content, storage \& distribution.\\
      - Miscellaneous adjustments.
      \item \textbf{Keywords:} Java EE, Tomcat, MySQL, Vaadin, Maven, Linux.
      \item \textbf{Web:} www.ppacarboncalculator.co.uk
    \end{rSubsection}

    \begin{rSubsection}{Vetenskapsrådet}{February 2012}{Digital compilation of annual grant reports - Software developer}{Stockholm}
      \item Compiled annual grant reports by writing a program that extracted grant data from an intranet database and composed it with other Excel data.
      \item \textbf{Keywords:} Java, Maven, Linux.
    \end{rSubsection}

    \begin{rSubsection}{Innventia AB}{July 2011 - November 2011}{PPA Carbon Calculator - Software developer}{Stockholm}
      \item Developed the PPA Carbon Calculator based on the Book Carbon Calculator platform created as part of bachelor's thesis.
      \item Tutored student intern in software development and agile methods.
      \item \textbf{Keywords:} Java EE, Tomcat, MySQL, Vaadin, Maven, Linux.
      \item \textbf{Web:} www.ppacarboncalculator.co.uk
    \end{rSubsection}
  \end{rSection}

  \newpage
  \begin{rSection}{Employment history}
  	{\bf Bytelope AB, Stockholm}
    \hfill {\em April 2021 - Present } \\
    { Permanent employment, full-time. }
    
  	{\bf Svensk Travsport AB, Stockholm}
    \hfill {\em June 2020 - March 2021 } \\
    { Permanent employment, full-time including on-call. }

    {\bf Combitech AB, Stockholm}
    \hfill {\em August 2012 - June 2020 } \\
    { Permanent employment, full-time. }

    {\bf Saab AB, Järfälla}
    \hfill {\em November 2012 - August 2016 } \\
    { Permanent employment, full-time. }

    {\bf Innventia AB, Stockholm}
    \hfill {\em February 2012 - July 2012 } \\
    { Project employment, part-time. }

    {\bf Academic Work AB, Stockholm}
    \hfill {\em January 2012 - November 2012 } \\
    { Permanent employment, full-time. }

    {\bf Innventia AB, Stockholm}
    \hfill {\em June 2011 - July 2011 } \\
    { Project employment, part-time. }
  \end{rSection}

  \begin{rSection}{Education}

  {\bf Informator AB}
    \hfill {\em 2019 (2 days) } \\
    { Agile Architecture Fundamentals [T1101] }

    {\bf Combitech Grow}
    \hfill {\em 2019 (2 days) } \\
    { Software Craftsmanship }

    {\bf Informator AB}
    \hfill {\em 2017 (2 days) } \\
    { Effective Coding Principles and Patterns in Java 8 [T1627] }

    {\bf EclipseSource GmbH}
    \hfill {\em 2014 (3 days) } \\
    { Advanced Eclipse RCP }

    {\bf LEAST Technical/Tactical consulting and Training}
    \hfill {\em 2013 (2 days)} \\
    { Evolution of Air Power – Tactics and connections to Technology }

    {\bf KTH Royal Institute of Technology}
    \hfill {\em 2007 - 2011 } \\
    { Completed 177 credits towards a BSc in Information and Communication Technology } \\
    {Thesis: BookCarbon: A system for tracking carbon dioxide emissions in the life cycle of a book}

    {\bf Cambridge Assessment English}
    \hfill {\em 2006 } \\
    { Cambridge English: Proficiency, Grade: B }

    {\bf International IT College of Sweden}
    \hfill {\em 2004 - 2007 } \\
    { Upper secondary school, Natural science program, specialization mathematics \& computer science}
  \end{rSection}

  \begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Languages  & Erlang, Golang, Groovy, Java, Javascript, Python, Shell                   \\
      Frameworks & Java EE, Spring Boot, Vert.x, Vaadin, Vue.js, TensorFlow                  \\
      Cloud      & Amazon Web Services (AWS), Google Cloud Platform (GCP), Microsoft Azure   \\
      Databases  & Cosmos DB, Elasticsearch, H2, MongoDB, Neo4j, Oracle Database, PostgreSQL \\
      Tools      & Docker, Git, Gradle, IntelliJ IDEA, JUnit, Kubernetes, Maven, Mockito     \\
      GitHub     & www.github.com/jahwag
    \end{tabular}
  \end{rSection}

\end{document}
